\chapter{Review of Related Literature}

\section{Zinc oxide}

\subsection{Crystal structure}

Zinc oxide is a metal oxide semiconductor having a hexagonal crystal structure.
In studies such as those of \citeA{gao08} and \citeA{fdoping}, there are three identified main peaks in the diffaction pattern of zinc oxide.
These three peaks are the first three peaks in the diffraction pattern of ZnO found roughly at $2\theta \in \{32\degg , 34\degg , 36\degg\}$.
The planes of diffraction are $(100)$, $(002)$, and $(101)$, respectively, with the highest peaks at the $(002)$ plane suggesting preferrential orientation in the \textit{c}-axis.
With regard to flat surfaces, this suggests formation of vertical rod-like structures from the substrates.

Numerous studies such as those of \citeA{gao08}, \citeA{vargas08}, and \citeA{fdoping} have shown experimentally that this structure of zinc oxide can be achieved even through production using different processes.
All of these showed that manipulating the processing parameters have various effects on the crystalline structure of the material.
They have effects on the crystallite size and relative intensities (diffraction).
It is worth noting that the processes used for fabrication are SILAR processes, as will be described in a later section.

The three SILAR processes analyzed by \citeA{vargas08} showed differences in the relative intensities of the diffraction peaks.
It can also be noted that some of the diffraction peaks present in films fabricated by a process were not found in another.
\citeA{fdoping} showed how different doping concentrations affected the overall crystallinity of the thin film structure.
The results, as expected, showed that different processing parameters lead to different material crystal structures.

\subsection{Electrical properties}

Studies have shown that zinc oxide thin films exhibit a wide variety of interesting properties such as  \emph{band gap} and \emph{electrical resistivity}.
Those of \citeA{fdoping} and \citeA{vargas08} made empirical studies on the effects of different processes on the electrical properties of ZnO.
Specifically, \citeA{fdoping} compared band gaps and electrical resistivity, while \citeA{vargas08} compared band gap.
Just as different processing parameters have led to differences in material crystal structures, the difference in crystal structures also reflect differences in material property.

Research on zinc oxide thin films as gas sensors by exploiting the reversible reactions of reducing gases to the surface of the material \cite{florido17}.
These surface reactions change the movement of charges within the crystal structures of materials affecting their \emph{resistivity}.
There are more literature that show how crystal structures affect the electrical resistivity and gas sensing response of metal oxide semiconductors from theoretical studies such as of \citeA{dey} and \citeA{powerlaw} to \textit{in silica} studies like involving DFT \cite{dft}.

The importance of being able to computationally predict the properties similar to the \textit{in silica} study referred to above is a huge milestone in predicting properties given the structure of a material.

\subsection{Successive ionic layer adhesion and reaction processes}

Successive ionic layer adhesion and reaction (SILAR) processes are a family of processes wherein materials are deposited onto substrates by means of successive surface reactions \cite{gao08}.
The processes consist of two main phases: a \emph{deposition} phase and an \emph{annealing} phase.
The deposition phase in material fabrication involves a set of precursor solutions: cationic solutions, complexing solutions, and anionic solutions, to perform the reactions on the surface of the substrate.
The three solutions are aqueous \cite{gao08}.
Thus, the substrate surface must be hydrophilic for the solutions to react in the and adhere.
However, naturally, glass is hydrophobic which can be noted by the formation of droplets on its surface.
\citeA{gao08} suggested the following methodology to develop the hydrophilic property of glass surface: boil the substrates in dilute $H_2SO_4$ ($1:10$ v/v) for $30$ minutes, then completely rinse the substrates in ethanol, acetone, and de-ionized water.
Similar processes were also done by \citeA{fdoping} and \citeA{vargas08}.

A study conducted by \citeA{vargas2} was performed in order to determine the effects of three different number of deposition cycles to thin film crystallinity.
It was observed that the relative intensities of the diffraction peaks drastically increased with the number of deposition cycles.
However, there was no literature, as of this manuscript, that can be used to explain this phenomenon.
It should be noted that the studies conducted by \citeA{vargas2} and \citeA{vargas08} differ in the parameter tested in SILAR processing.

In addition to the precursor solutions and substrate properties described, another factor that affects the output of SILAR processes is the drying interval being deployed between each dipping processes \cite{gao08}.
In the cited literature, the researchers compared the effects of two drying processes in the crystallinity of the thin films.
In applying a drying process of $3-5$ or $30$ seconds between each deposition \emph{cycle}, the resulting thin films have a defined and \emph{periodic} microstructure.
Those films processed with no drying process between each deposition cycle were found to have \emph{amorphous} microstructures.

The annealing process in SILAR processes is crucial for the growth of crystal structures in the thin film.
According to \citeA{fdoping}, it is still unknown how, specifically, annealing affects this growth.
There are numerous \emph{empirical} studies regarding this topic, however, there is currently no solid theory known to the researchers as of date.

In the study of \citeA{fdoping}, it can be observed through the XRD spectra that annealing plays a huge role in the development of crystal structures.
It can be seen that the measured intensities at the Bragg angles stated above have increased.
This means that better crystallinity is achieved through thermal annealing.
The study of \citeA{gao08} has found that there can also be different effects on thin film crystallinity based on the annealing environment used.
It can be inferred from the data that the adjusting the annealing environment leads to different average crystallite sizes within the thin films.

Studies by \citeA{vargas08}, \citeA{vargas2}, \citeA{gao08}, and \citeA{fdoping} all have used different precursor solutions in preparing thin films.

\section{Multiscale Modeling}

\subsection{Representative volume elements}

Crucial in most multiscale modeling methodologies is the development of elements of finite volume that reflects the general physics of the macrostructure.
Representative volume elements (RVE) are images of the material chosen such that the overall distribution of the \emph{local states} and their interactions may be able to represent the underlying mechanisms (physics) of the whole structure at a particular length scale.
For reference, definitions are as follows \cite{bone,bunge,cnn,gupta15,polar,sun17,yabansu14}: the probe volume ($S$) represents the material volume to be studied, it is the same as the RVE of interest, a voxel ($s$) is a small, discrete volume element taken from $S$, the local state space $H$ is the set of all realizable physical and chemical properties representing material characteristics a local state $h$ is an element of $H$, finally boundary conditions $\aleph$ are a set of requirements for interactions within $S$.

These definitions are important in establishing concepts regarding the use of RVEs in different property homogenization models.
As will be seen in later discussions, $S$ and $\aleph$, but not $s, H, h$, will have slightly varied definitions depending on the data needed by specific modeling techniques.

\subsection{Finite element methods}

Finite element methods rely on computer simulations of mechanical theories on finite, discrete elements $s \in S$.
This means that this method can be used to simulate and study the effects of mechanical systems with respect to space and their interactions with one another.
An interesting study done by \citeA{bone} dealt with finding an optimal $\aleph$, with regard to the case, conditions to be met incorporating the interaction of collagen fibers ($h_1 \in H$) and the surrounding cellular matrix ($h_2 \in H$).
In finite element considerations, however, these are not the only conditions that must be followed.
Energy conformation conditions also have to be observed \cite{cosserat}.

The work of \citeA{cosserat} dealt with the establishment of a mathematical derivation of a model for microstate property homogenization.
Their work, split into six sections of rigorous mathematical manipulation, involves these steps: expression of Cauchy continuum energy and mechanical conformation conditions into Cosserat continuum conditions, the development of a homogenization model, and establishment of $\aleph$.
The steps in proof done by these researchers present a method in developing homogenization models using different representations of an RVE.
It is worth noting that the definition of the RVE is flexible for as long as proper conditions are imposed.

These finite element methods are \emph{very} effective in modeling the interactions of different materials and their configurations within an RVE \cite{bone,cosserat}.
Due to the complexity of the implementation of this method, computer simulations may run for hours, which is not efficient in rapid, high-throughput materials processing \cite{cnn}.

\subsection{Deep learning methods}

With the development of the various fields of artificial intelligence, many different modeling techniques have been developed, especially in the areas of image recognition, and multivariable property prediction with the use of convolutional and artifical neural networks \cite{cnn}.
A homogenization model was developed by \citeA{cnn} for predicting the ionic conductivity of ceramics using convolutional neural networks.
The research was done in order to determine the feasibility of using convolutional neural networks in microstructure image processing, and to predict the desired property from image analyses.

The RVEs used by the CNN are \emph{raw} images of the material at particular length scales.
The researchers aimed to determine how the length scale of the RVE affected the accuracy of their model.
Note that the computer images are analyzed through discrete elements $s$ as image pixels.
The study used a completely different representation of RVEs from those used by finite element studies such as of \citeA{bone} and \citeA{cosserat}.
In the study it has been found that it is possible to perform image analysis on a small number of RVEs with a definite size (enough to distinguish between different $h$).
The researchers were able to only use seven images in the prediction of the property of interest with ``acceptable'' accuracy.

One of the problems with using advanced artificial intelligence methodologies, as admitted by \citeA{cnn}, was the uninterpretability of the model.
In order to circumvent this problem and to provide a basis for model classification and prediction, the researchers have provided ``saliency maps'' to see how the CNN classified the local states and inferred the interaction of such local states through implicit $\aleph$.
This may be a good protocol on studying how CNNs work internally and provide a one-way theories to predict desired properties.

Another problem posed by the use of CNNs, not mentioned in the research, is the unidirectional flow of information.
As evident from the research, the desired property, given different RVEs can be calculated; however, even with the introduction of saliency maps as above study described, it may still be difficult to reconstruct an RVE and its processing history from the properties desired.
This is the case with most engineering problems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Materials knowledge systems}

\subsection{Microstructure functions}

The materials knowledge framework is a data science framework developed for the relatively simple modeling of material process, structure, and property.
This framework will be the modeling methodology of interest of the study.
A careful review of the data analysis framework will be given as follows.

The materials knowledge systems (MKS) framework rests upon the definition of microstructure functions.
This probability density function ($m(\vec{x}, h)$) has the following properties \cite{delin}:

\[
  m(\vec{x}, h)dH = \dfrac{^{h}V}{V}\biggr\rvert_{\vec{x}}
\]

This means that the probability density of finding a local state $dH = h$ can be expressed as the volume fraction of the $h$ within $V = dS$.
By summing over the local state space $H$, the probability should add up to $1$ by definition of the local state space.

\[
  \int_H m(\vec{x}, h)dH = 1
\]

From these descriptions, analogous expressions can be defined for discrete data.

\[
  \sum_{S} {^hm_s} = ^hV\lvert S\rvert \hspace{1in}
  \sum_{h=1}^{H} {^hm_s} = 1
\]

The probability function $^hm_s$ gives the volume fraction occupied (the expected probability) of the local state defined by $h$ in the voxel $s$.

With the definition of discrete microstructure functions, it is possible \emph{for computers} to perform calculations from various data relating to RVEs.
Operations on probabilities and images may be applied.
Examples of these operations include calculation of spatial statisitics (\textit{N}-point spatial correlations), which have been used in quite a number of studies.
In each of these studies, there appears to be a different method for defining $h_i$, and hence $H$, depending on the properties being studied in materials.

Studies conducted by \citeA{yabansu14}, \citeA{delin}, \citeA{bunge}, and \citeA{sun17} have used different methods in defining the local state space $H$ depending on which definition will yield more \emph{computationally efficient} results.
The ones cited are studies on two-phase material systems, polycrystalline systems, and other composite material systems.

\citeA{sun17} studied dendritic structures in a \emph{two-phase} non-parallelepiped RVEs.
They have shown through a case study that it is possible to apply different image processing techniques such as image masking and padding for the calculation of spatial correlations from modified microstructure functions.
They have done this through the introduction of padding modifications and masking functions, which directly change the algorithm for the calculation of spatial correlations.
In this two-phased material structure, given that image resolution is fine enough, states $h_0$ and $h_1$, \emph{eigenstates}, are assigned to the voxels $s \in S$.
These eigenstates are defined by the presence $h_1 = 1$ or absence $h_0 = 0$ of the state of interest.

The use of $h_1$ for the identification of a local state $h$ indicates that $h_1$ occupies the entirety of $s$, while $h_0$ is used for representing the other local state.
One problem as noted of this classification is the fact that the definition of $H$ may be based on researcher bias \cite{cnn}.

\citeA{yabansu14} and \citeA{bunge} did studies on the possible prediction of properties in polycrystalline material systems with the use of the MKS framework.
Since both studies have noticed the tremendous amount of local state representation using Euler-Bunge angles, they have decided to use generalized spherical harmonics to define $H$.
With these efforts, the computations were drastically reduced!
The method used will not be discussed in detail for it is outside the scope and applications of the study.

\citeA{delin} worked on the delineation of the properties of spatial correlations in multiphase composite systems.
They have introduced the concept of \emph{hulls} such as one-point and two-point spatial correlation hulls that define the physically realizable spatial correlations given the training dataset.

Discrete microstructure functions $^hm_s$ explain \emph{only} the probability density of finding local states $h$ at small voxels $s$ \cite{polar}.
They have also remarked that the measure is not \textit{translation-invariant}, \textit{i.e., assumptions in statistics are not directly applicable}.
This can be circumvented by the definition of \emph{N-point statistics} such as one-point and two-point spatial correlations as will be discussed for the next subsections.

\subsection{One-point spatial correlations}

One-point spatial correlations define the expected probability of the local state to appear in the whole RVE.
This is equivalent to the \emph{volume fraction} occupied by a certain $h$ for in $S$ \cite{delin}.
By rearrangement of an equation above:

\[
  f(h) = \dfrac{1}{\lvert S\rvert} \sum_{S} {^hm_s} = {^hV}
\]

Using the microstructure functions themselves, the one-point statistic for a discrete distinguishable $h$ is the \emph{volume average} of the probability.
The calculation of the this statistic is easy and increases linearly with respect to the size of the RVE.

\subsection{Two-point spatial correlations}

Two-point correlations are a type of N-point statistics that define the \emph{joint probability} of locating two local states within voxels $s$ separated by a displacement vector $\vec{t}$ \cite{delin}.
Usually, to define these statistics and easily evaluate them, the vectors are assigned into indices from $0$ to $\lvert S-1\rvert$.
The ``translation-invariant'' two-point spatial correlations are defined as:

\[
  f(hh'\lvert t) = \dfrac{1}{\lvert S\rvert}\sum_{t \in S} {^hm_s} \cdot ^{h'}m_{s+t}
\]

The studies mentioned above, including \citeA{polar}, have different methods of calculating two-point spatial correlations because of the difference in definition of the microstructure function.

\subsubsection{Calculation of values}

All of the cited literature on the topic similarly defined two-point spatial correlations as a \emph{convolution} operation on two probability densities.
They all have exploited the transformation of the microstructure function into spectral space via discrete Fourier transforms (DFT).
The properties of complex numbers have been exploited in many different ways by the cited literature in calculating the said statistics \cite{delin,polar,sun17,bunge,yabansu14}.

The calculations in spectral space have been shown to have drastically reduced time complexities \cite{delin}.
\citeA{polar} used the expression of complex numbers in polar form to describe ``rotationally invariant'' spatial correlations in spectral space.
The use of mask functions and padding operations \cite{sun17} redefined the calculations of two-point statistics in non-parallelepiped material systems.
The use of Bunge-Euler angles in the reduction of local states \cite{bunge, yabansu14} were helpful in reducing the amount of calculations needed.
